### 2022-11-14 Draft2.Rmd
progress

```{r}
# Loading all necessary packages
library(tidyverse)
library(dplyr)
library(tidymodels)
library(readr)
# Assigning the data to a variable
pokemon <- read_csv("data/pokemon.csv")
tidymodels_prefer()
set.seed(0124)
```

@@

@@

>>>>

```{r}
# Loading all necessary packages
library(tidyverse)
library(dplyr)
library(tidymodels)
library(readr)
library(kknn)
# Assigning the data to a variable
pokemon <- read_csv("data/pokemon.csv")
tidymodels_prefer()
set.seed(0124)
```

@@

### Linear Regression

@@

### Polynomial Regression

### Ridge Regression   
```{r}
ridge_lasso_recipe <- recipe(capture_rate ~ attack + defense + hp + sp_attack + sp_defense + speed + type1 + generation + is_legendary + has_sturdy + has_swift_swim + has_keen_eye + has_chlorophyll + has_levitate, data = pokemon_train) %>%
  step_dummy(all_nominal_predictors()) %>% 
  step_novel(all_nominal_predictors()) %>% 
  step_zv(all_predictors()) %>% 
  step_normalize(all_predictors())

ridge_spec <- linear_reg(mixture = 0, penalty = tune()) %>% 
  set_mode("regression") %>% 
  set_engine("glmnet")

ridge_workflow <- workflow() %>% 
  add_recipe(ridge_lasso_recipe) %>% 
  add_model(ridge_spec)

penalty_grid <- grid_regular(penalty(range = c(-5,5)), levels = 50)

tune_res <- tune_grid(
  ridge_workflow,
  resamples = pokemon_folds,
  grid = penalty_grid
)
```
```{r}
autoplot(tune_res)
```

```{r}
best_penalty <- select_best(tune_res, metric = "rsq")

ridge_final <- finalize_workflow(ridge_workflow, best_penalty)
ridge_final_fit <- fit_resamples(ridge_final, resamples = pokemon_folds)
collect_metrics(ridge_final_fit)
```

### Lasso Regression 
```{r}
lasso_spec <- 
  linear_reg(penalty = tune(), mixture = 1) %>% 
  set_mode("regression") %>% 
  set_engine("glmnet")

lasso_workflow <- workflow() %>% 
  add_recipe(ridge_lasso_recipe) %>% 
  add_model(lasso_spec)

tune_res2 <- tune_grid(
  lasso_workflow,
  resamples = pokemon_folds,
  grid = penalty_grid
)
```

```{r}
autoplot(tune_res2)
```

```{r}
best_lasso_penalty <- select_best(tune_res2, metric = "rsq")
lasso_final <- finalize_workflow(lasso_workflow, best_lasso_penalty)
lasso_final_fit <- fit_resamples(lasso_final, resamples = pokemon_folds)
```

```{r}
collect_metrics(lasso_final_fit)
```

```{r, message = FALSE, warning = FALSE}
poly_rec <- recipe(capture_rate ~ attack + defense + hp + sp_attack + sp_defense + speed + type1 + generation + is_legendary + has_sturdy + has_swift_swim + has_keen_eye + has_chlorophyll + has_levitate, data = pokemon_train) %>%
  step_dummy(all_nominal_predictors()) %>%
  step_poly(all_numeric_predictors(), degree = tune())

#step_poly(sp_attack, degree = 2) %>% 
 # step_poly(defense, degree = 2) %>% 
  #step_poly(sp_defense, degree = 2) %>% 
#  step_poly(hp, degree = 2) %>% 
 # step_poly(speed, degree = 2)

lm_spec <- linear_reg() %>% 
  set_mode("regression") %>% 
  set_engine("lm")

poly_wf <- workflow() %>% 
  add_model(lm_spec) %>% 
  add_recipe(poly_rec)

degree_grid <- grid_regular(degree(range = c(1,5)), levels = 5)

tune_res3 <- tune_grid(
  poly_wf,
  resamples = pokemon_folds,
  grid = degree_grid
)
autoplot(tune_res3)
```

### KNN  
```{r}
knn_model <- nearest_neighbor(
  neighbors = tune(),
  mode = "regression") %>% 
  set_engine("kknn")

knn_workflow <- workflow() %>% 
  add_model(knn_model) %>% 
  add_recipe(pokemon_recipe)

knn_parameters <- parameters(knn_model)

knn_grd <- grid_regular(knn_parameters, levels = 5)

knn_tune <- tune_grid(
    knn_workflow,
    resamples = pokemon_folds,
    grid = knn_grd
  )
```

```{r}
best_knn <- select_best(knn_tune, metric = "rmse")
knn_final <- finalize_workflow(knn_workflow, best_knn)
knn_final_fit <- fit_resamples(knn_final, resamples = pokemon_folds)
```

```{r}
collect_metrics(knn_final_fit)
```
